---
title: "Set up for a Methodological Review Board in Psychology at the University of Padova"
authors: "L. Sità, M. Manente, A. Perugini, G. Calignano, E. Toffalini, I. Alfarone, T. Marci, M. Pastore, G. Altoè"
format: 
  revealjs:
    center: true
    logo: "Psicostat_LOGO.png"
    embed-resources: true
    slide-number: true
    toc: true
    toc-title: "Content"
    footer: "PYMS June 5th 2025 - ambra.perugini@phd.unipd.it"
    theme: simple
cache: true
include-in-header:
  - text: |
      <style>
      #title-slide .title {
        font-size: 2em;
        color: #9B0014;
      }
      .slide-logo {
        height: 60px !important;
        max-height: none !important;
        position: absolute !important;
        bottom: 10px !important;
        right: 10px !important;
        top: unset !important;
        left: unset !important;
      }
      </style>

---



```{r setup}
#| echo: false
rm(list= ls())
library(here)
library(readxl)
library(ggplot2)
library(dplyr)
library (patchwork)
library(tm)
library(wordcloud)
library(jcolors)

######################################## Importazione Dataset

dataMRB <- read_excel(here("/Users/ambraperugini/Documents/Work/Conferences/Presentazioni/PYMS_2025/dati.xlsx"))
dataMRB <- data.frame(dataMRB)

######################################## DATACLEANING

## 1.1. Eliminazione di righe == preview (compilazioni pre-15 aprile), 
## questionari non completi
## prime due righe ridondanti

datacleaned <- dataMRB[-(c(1:12, 62, 67)), -(c(2:6,8:17))]
datacleaned <- datacleaned [datacleaned$Finished == "True",]

## Rinominazione degli item ID

item_renamed <- matrix(data = c("Start date", "Finished", 1, 2.1, 2.2, 2.3, 2.4,
                                2.5, 3, 4, 5, 6.1, 6.2, 6.3, 6.4, 6.5, 6.6,
                                6.7, 7.1, 7.2, 7.3, 8.1, 8.2, 8.3, 8.4, 8.5, 
                                8.6, 9.1, 9.2, 9.3, 10.1, 10.2, 10.3, 10.4,
                                10.5, 11.1, 11.2, 11.3, 12.1, 12.2, 13.1, 
                                13.2, 13.3, 13.4, 13.5, 14, 15, 16
                                ), 1, 48)

colnames(datacleaned) <- as.character(datacleaned[1, ])  # Set first row as column names
colnames(datacleaned) <- item_renamed

## Rinominazione righe
# row_renamed <- matrix(data = c(1:53), nrow = 53, ncol = 1)
# rownames(datacleaned) <- as.character(datacleaned[,1])
# rownames (datacleaned) <- row_renamed

for (i in 22:27) {
datacleaned[[i]] <- ifelse(datacleaned[[i]] == "No, mai", "No, never", ifelse(datacleaned[[i]] == "Sì, ma non l'ho gestito personalmente", "Yes, but I didn't handle it personally", ifelse(datacleaned[[i]] == "Sì, l'ho gestito personalmente", "Yes, I handled it personally",datacleaned[[i]])  ))
}


######################################## FUNZIONI DESCRITTIVE AGGREGATE

## Funzione per plot frequenze
require(ggplot2)

plot_frequenze <- function(colonna, titolo) {
  
  datacleaned[[colonna]] <- ifelse(datacleaned[[colonna]] == "Sì", "Yes",
                                   datacleaned[[colonna]])
  
  dati_filtrati <- datacleaned[!is.na(datacleaned[[colonna]]), ]
  
  if (nrow(dati_filtrati) == 0) {
    warning("Nessun dato disponibile per il grafico.")
    return(NULL)
  }
  
  freq_table <- as.data.frame(table(Risposta = dati_filtrati[[colonna]]))
  colnames(freq_table)[2] <- "Frequenza"
  freq_table$Percentuale <- (freq_table$Frequenza / sum(freq_table$Frequenza)) * 100
  N <- sum(freq_table$Frequenza)

  ggplot(freq_table, aes(x = Risposta, y = Percentuale)) +
    geom_col(width = 0.7, fill = "#4682B4", show.legend = FALSE) +
    geom_text(aes(label = paste0("n=", Frequenza)), vjust = -0.4, size = 4.5) +
    labs(
      title = titolo,
      subtitle = paste("N =", N),
      x = "Response",
      y = "Percentage"
    ) +
    scale_y_continuous(breaks = seq(0, 100, by = 5)) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}


## Funzione per likert "Per niente-Molto"

plot_likert_molto <- function(colonna, titolo) {
  dati <- datacleaned[[colonna]]

  mappa_likert <- c(
    "Per niente" = "Not at all", "per niente" = "Not at all",
    "Poco" = "Not much", "poco" = "Not much",
    "Abbastanza" = "A bit", "abbastanza" = "A bit",
    "Molto" = "Very much", "molto" = "Very much"
  )
  
  dati_raggruppati <- mappa_likert[as.character(dati)]
  dati_raggruppati <- dati_raggruppati[!is.na(dati_raggruppati) & dati_raggruppati != ""]
  
  livelli_ordinati <- c("Not at all", "Not much", "A bit", "Very much")
  dati_fattore <- factor(dati_raggruppati, levels = livelli_ordinati, ordered = TRUE)
  
  freq_table <- as.data.frame(table(Risposta = dati_fattore))
  colnames(freq_table)[2] <- "Frequenza"
  freq_table$Percentuale <- (freq_table$Frequenza / sum(freq_table$Frequenza)) * 100
  N <- sum(freq_table$Frequenza)

  ggplot(freq_table, aes(x = Risposta, y = Percentuale)) +
    geom_col(width = 0.7, fill = "#4682B4", show.legend = FALSE) +
    geom_text(aes(label = paste0("n=", Frequenza)), vjust = -0.4, size = 5.2) +
    labs(
      title = titolo,
      subtitle = paste("N =", N),
      x = "Response",
      y = "Percentage"
    ) +
    scale_x_discrete(drop = FALSE, limits = livelli_ordinati) +
    scale_y_continuous(breaks = seq(0, 100, by = 5)) +
    theme_minimal(base_size = 15) +
    theme(
      plot.title = element_text(face = "bold", size = 17, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}



## Funzione likert "Per niente-Completamente"

plot_likert_completamente <- function(colonna, titolo) {
  dati <- datacleaned[[colonna]]

  mappa_likert_1 <- c(
    "Per niente" = "Not at all", "per niente" = "Not at all",
    "Poco" = "Not much", "poco" = "Not much",
    "Abbastanza" = "A bit", "abbastanza" = "A bit",
    "Completamente" = "Completely", "completamente" = "Completely"
  )

  dati_raggruppati <- mappa_likert_1[as.character(dati)]
  dati_raggruppati <- dati_raggruppati[!is.na(dati_raggruppati) & dati_raggruppati != ""]
  
  livelli_ordinati <- c("Not at all", "Not much", "A bit", "Completely")
  dati_fattore <- factor(dati_raggruppati, levels = livelli_ordinati, ordered = TRUE)

  freq_table <- as.data.frame(table(Risposta = dati_fattore))
  colnames(freq_table)[2] <- "Frequenza"
  freq_table$Percentuale <- (freq_table$Frequenza / sum(freq_table$Frequenza)) * 100
  N <- sum(freq_table$Frequenza)

  ggplot(freq_table, aes(x = Risposta, y = Percentuale)) +
    geom_col(width = 0.7, fill = "#4682B4", show.legend = FALSE) +
    geom_text(aes(label = paste0("n=", Frequenza)), vjust = -0.4, size = 5.2) +
    labs(
      title = titolo,
      subtitle = paste("N =", N),
      x = "Response",
      y = "Percentage"
    ) +
    scale_x_discrete(drop = FALSE, limits = livelli_ordinati) +
    scale_y_continuous(breaks = seq(0, 100, by = 5)) +
    theme_minimal(base_size = 15) +
    theme(
      plot.title = element_text(face = "bold", size = 17, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}



######################################## FUNZIONI DESCRITTIVE DISAGGREGATE


## Rinominare gruppi Strutturati e Non-strutturati
datacleaned$Gruppo <- ifelse(datacleaned$"1" %in% c("PO, PA, RTD, RTT"), "Tenure track",
                             ifelse(datacleaned$"1" %in% c("Dottorato, assegno di ricerca"), "ECRs", NA))


## Funzione per grafico tasso di risposta
plot_tasso_risposta <- function(totali_strutturati, totali_non_strutturati, titolo = "") {
  
  # Calcolo delle risposte ricevute per ciascun gruppo
  risposte_strutturati <- sum(datacleaned$Gruppo == "Tenure track", na.rm = TRUE)
  risposte_non_strutturati <- sum(datacleaned$Gruppo == "ECRs", na.rm = TRUE)
  
  # Creazione del dataframe per il grafico
  df <- data.frame(
    Gruppo = c("Tenure track", "ECRs"),
    Risposte = c(risposte_strutturati, risposte_non_strutturati),
    Totali = c(totali_strutturati, totali_non_strutturati)
  )
  
  # Calcolo del tasso di risposta
  df$Percentuale <- (df$Risposte / df$Totali) * 100
  
  # Creazione del grafico
  ggplot(df, aes(x = Gruppo, y = Percentuale, fill = Gruppo)) +
    geom_col(width = 0.7) +
    geom_text(aes(label = paste0("n=", Risposte)), vjust = -0.4, size = 4.5) +
    labs(
      title = titolo,
      subtitle = paste("Total: Tenure track =", totali_strutturati, ", ECRs =", totali_non_strutturati),
      x = "Group",
      y = "Percentage of response"
    ) +
    scale_y_continuous(breaks = seq(0, 100, by = 5), limits = c(0, 100)) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}


## Funzione per visualizzazione dati disaggregati (dicotomiche)

plot_confronto_gruppi <- function(colonna, titolo) {
  
    datacleaned[[colonna]] <- ifelse(datacleaned[[colonna]] == "Sì", "Yes",
                                   datacleaned[[colonna]])

  datacleaned$Gruppo <- ifelse(datacleaned$"1" %in% c("PO, PA, RTD, RTT"), "Tenure Track",
                               ifelse(datacleaned$"1" %in% c("Dottorato, assegno di ricerca"), "ECRs", NA))

  dati_filtrati <- datacleaned[!is.na(datacleaned[[colonna]]) & !is.na(datacleaned$Gruppo), ]
  if (nrow(dati_filtrati) == 0) {
    warning("Nessun dato disponibile per il grafico.")
    return(NULL)
  }

  freq_table <- as.data.frame(table(Risposta = dati_filtrati[[colonna]], Gruppo = dati_filtrati$Gruppo))
  colnames(freq_table)[3] <- "Frequenza"

  totali <- aggregate(Frequenza ~ Gruppo, data = freq_table, sum)
  freq_table <- merge(freq_table, totali, by = "Gruppo", suffixes = c("", "_Totale"))
  freq_table$Percentuale <- (freq_table$Frequenza / freq_table$Frequenza_Totale) * 100

  ggplot(freq_table, aes(x = Risposta, y = Percentuale, fill = Gruppo)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    geom_text(aes(label = paste0("n=", Frequenza)),
              position = position_dodge(width = 0.8), vjust = -0.4, size = 4.5) +
    labs(
      title = titolo,
      subtitle = paste("N =", sum(freq_table$Frequenza)),
      x = "Response",
      y = "Percentage",
      fill = "Gruppo"
    ) +
    scale_y_continuous(breaks = seq(0, 100, by = 5)) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}


## Funzione per dati disaggregati - Likert "Per niente-Molto"

plot_likert_gruppi_molto <- function(colonna, titolo) {
  datacleaned$Gruppo <- ifelse(datacleaned$"1" %in% c("PO, PA, RTD, RTT"), "Tenure track",
                               ifelse(datacleaned$"1" %in% c("Dottorato, assegno di ricerca"), "ECRs", NA))

  mappa_likert <- c(
    "Per niente" = "Not at all", "per niente" = "Not at all",
    "Poco" = "Not much", "poco" = "Not much",
    "Abbastanza" = "A bit", "abbastanza" = "A bit",
    "Molto" = "Very much", "molto" = "Very much"
  )
  livelli_ordinati <- c("Not at all", "Not much", "A bit", "Very much")

  dati_filtrati <- datacleaned[!is.na(datacleaned[[colonna]]) & !is.na(datacleaned$Gruppo), ]
  dati_filtrati$Risposta <- mappa_likert[as.character(dati_filtrati[[colonna]])]
  dati_filtrati <- dati_filtrati[!is.na(dati_filtrati$Risposta) & dati_filtrati$Risposta != "", ]
  dati_filtrati$Risposta <- factor(dati_filtrati$Risposta, levels = livelli_ordinati, ordered = TRUE)

  freq_table <- as.data.frame(table(dati_filtrati$Risposta, dati_filtrati$Gruppo))
  colnames(freq_table) <- c("Risposta", "Gruppo", "Frequenza")

  totali <- aggregate(Frequenza ~ Gruppo, data = freq_table, sum)
  freq_table <- merge(freq_table, totali, by = "Gruppo", suffixes = c("", "_Totale"))
  freq_table$Percentuale <- (freq_table$Frequenza / freq_table$Frequenza_Totale) * 100

  ggplot(freq_table, aes(x = Risposta, y = Percentuale, fill = Gruppo)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    geom_text(aes(label = paste0("n=", Frequenza)),
              position = position_dodge(width = 0.8), vjust = -0.4, size = 5) +
    labs(
      title = titolo,
      subtitle = paste("N =", sum(freq_table$Frequenza)),
      x = "Response",
      y = "Percentage",
      fill = "Gruppo"
    ) +
    scale_x_discrete(drop = FALSE, limits = livelli_ordinati) +
    scale_y_continuous(breaks = seq(0, 100, by = 5)) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}


## Funzione per dati disaggregati - Likert "Per niente-Completamente"

plot_likert_gruppi_completamente <- function(colonna, titolo) {
  datacleaned$Gruppo <- ifelse(datacleaned$"1" %in% c("PO, PA, RTD, RTT"), "Tenure track",
                               ifelse(datacleaned$"1" %in% c("Dottorato, assegno di ricerca"), "ECRs", NA))

  mappa_likert <- c(
    "Per niente" = "Not at all", "per niente" = "Not at all",
    "Poco" = "Not much", "poco" = "Not much",
    "Abbastanza" = "A bit", "abbastanza" = "A bit",
    "Completamente" = "Completely", "completamente" = "Completely"
  )
  livelli_ordinati <- c("Not at all", "Not much", "A bit", "Completely")

  dati_filtrati <- datacleaned[!is.na(datacleaned[[colonna]]) & !is.na(datacleaned$Gruppo), ]
  dati_filtrati$Risposta <- mappa_likert[as.character(dati_filtrati[[colonna]])]
  dati_filtrati <- dati_filtrati[!is.na(dati_filtrati$Risposta) & dati_filtrati$Risposta != "", ]
  dati_filtrati$Risposta <- factor(dati_filtrati$Risposta, levels = livelli_ordinati, ordered = TRUE)

  freq_table <- as.data.frame(table(dati_filtrati$Risposta, dati_filtrati$Gruppo))
  colnames(freq_table) <- c("Risposta", "Gruppo", "Frequenza")

  totali <- aggregate(Frequenza ~ Gruppo, data = freq_table, sum)
  freq_table <- merge(freq_table, totali, by = "Gruppo", suffixes = c("", "_Totale"))
  freq_table$Percentuale <- (freq_table$Frequenza / freq_table$Frequenza_Totale) * 100

  ggplot(freq_table, aes(x = Risposta, y = Percentuale, fill = Gruppo)) +
    geom_col(position = position_dodge(width = 0.8), width = 0.7) +
    geom_text(aes(label = paste0("n=", Frequenza)),
              position = position_dodge(width = 0.8), vjust = -0.4, size = 5) +
    labs(
      title = titolo,
      subtitle = paste("N =", sum(freq_table$Frequenza)),
      x = "Response",
      y = "Percentage",
      fill = "Gruppo"
    ) +
    scale_x_discrete(drop = FALSE, limits = livelli_ordinati) +
    scale_y_continuous(breaks = seq(0, 100, by = 5)) +
    theme_minimal(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
      axis.title.x = element_text(face = "bold"),
      axis.title.y = element_text(face = "bold"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10)
    )
}

```

# Methodological Review Board (MRB)

## Why the need for a MRB?

- Need for a cultural shift towards better research practices, starting from our department ^[Department of Developmental and Social Psychology, University of Padova]

- Lack of a review process in most pre-registrations

- Increasing demand for transparency and Open Science


## Project Goals

**Establish a sustainable MRB by**:

- Supporting clarity and transparency in pre-registration

- Offering advisory methodological feedback

- Maintaining impartiality (e.g., MRB members will not be listed as co-authors)

- Encouraging Open Science practices

## MRB characteristics 

- Voluntary submission to the MRB

- Advisory only, not gate-keeping

- Diverse expert reviewers (Statisticians, Psychometricians, Experts of the specific Psychological field)

- Not a tailored revision of the project, more of a quality check (i.e., sample size justification, clear hypothesis, planned data analysis)


## The MRB Workflow

1. Authors identify an appropriate pre-registration template (e.g. OSF)

2. Authors complete the chosen template and submit it to the MRB

3. Review and Feedback (multiple rounds if needed)

4. Pre-registration Submission

5. Final Check and Badge Award (if standards are met)

## Long-Term Impact Goals

- Monitor change in pre-registration rates among published studies over time

- Success will be defined as exceeding a 10% pre-registration rate among eligible studies within the first two years

- Promoting a culture of preregistration, transparency, open science and and fostering better research practices

# The Survey

## Department insight

- Attitudes toward preregistration and Open Science

- Perceived usefulness and feasibility of MRB

- Differences between Early Career Researchers (ECRs) and Tenure Track faculty members.


## Response rate

Total respondents: 53 out of `r 65+77`  (representing approximately `r round(53/(65+77)*100,0)`\% of the department’s academic staff).

- Tenure-track: 31 out of 65

- ECRs: 22 out of 77

BIAS?

## Have you ever heard about the replicability crisis? {.unlisted}

```{r scr4a}
plot_frequenze("4", "")
```

## Have you ever heard about the replicability crisis? {.unlisted}

```{r scr4b}
plot_confronto_gruppi("4", "")
```

## If so, do you think it's a problem for scientific progress? {.unlisted}

```{r scr5a}
plot_frequenze("5", "")
```

## If so, do you think it's a problem for scientific progress? {.unlisted}

```{r scr5b}

plot_confronto_gruppi("5", "")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.1a}
plot_likert_molto("6.1", "Outdated methods")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.1b}
plot_likert_gruppi_molto("6.1", "Outdated methods")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.2a}
plot_likert_molto("6.2", "Poor data quality")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.2b}
plot_likert_gruppi_molto("6.2", "Poor data quality")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.3a}
plot_likert_molto("6.3", "Lack of external validity")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.3b}
plot_likert_gruppi_molto("6.3", "Lack of external validity")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.4a}
plot_likert_molto("6.4", "Lack of internal validity")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.4b}
plot_likert_gruppi_molto("6.4", "Lack of internal validity")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.5a}
plot_likert_molto("6.5", "Publication Bias ")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.5b}
plot_likert_gruppi_molto("6.5", "Publication Bias")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.6a}
plot_likert_molto("6.6", "DoF of the Researcher")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.6b}
plot_likert_gruppi_molto("6.6", "DoF of the Researcher")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.7a}
plot_likert_molto("6.7", "Fraud ")
```

## How much do you think those are the causes? {.unlisted}

```{r scr6.7b}
plot_likert_gruppi_molto("6.7", "Fraud")
```


## Have you ever heard of those practices? {.unlisted}

```{r os7.1a}
plot_frequenze("7.1", "Pre-registration of Hypotheses")
```

## Have you ever heard of those practices? {.unlisted}

```{r os7.1b}
plot_confronto_gruppi("7.1", "Pre-registration of Hypotheses")
```

## Have you ever heard of those practices? {.unlisted}

```{r os7.2a}
plot_frequenze("7.2", "Pre-registration of Analyses")
```

## Have you ever heard of those practices? {.unlisted}

```{r os7.2b}
plot_confronto_gruppi("7.2", "Pre-registration of Analyses")
```

## Have you ever heard of those practices? {.unlisted}

```{r os7.3a}
plot_frequenze("7.3", "Registered Report ")
```

## Have you ever heard of those practices? {.unlisted}

```{r os7.3b}
plot_confronto_gruppi("7.3", "Registered Report")
```

## Have you ever used those practices? {.unlisted}

```{r os8.1a}
plot_frequenze("8.1", "Pre-registration of Hypotheses")
```

## Have you ever used those practices? {.unlisted}

```{r os8.1b}
plot_confronto_gruppi("8.1", "Pre-registration of Hypotheses")
```

## Have you ever used those practices? {.unlisted}

```{r os8.2a}
plot_frequenze("8.2", "Pre-registration of Analyses")
```

## Have you ever used those practices? {.unlisted}

```{r os8.2b}
plot_confronto_gruppi("8.2", "Pre-registration of Analyses")
```

## Have you ever used those practices? {.unlisted}

```{r os8.3a}
plot_frequenze("8.3", "Registered Report ")
```

## Have you ever used those practices? {.unlisted}

```{r os8.3b}
plot_confronto_gruppi("8.3", "Registered Report")
```

## Have you ever used those practices? {.unlisted}

```{r os8.4a}
plot_frequenze("8.4", "Open Materials ")
```

## Have you ever used those practices? {.unlisted}

```{r os8.4b}
plot_confronto_gruppi("8.4", "Open Materials")
```

## Have you ever used those practices? {.unlisted}

```{r os8.5a}
plot_frequenze("8.5", "Open Code ")
```

## Have you ever used those practices? {.unlisted}

```{r os8.5b}
plot_confronto_gruppi("8.5", "Open Code")
```

## Have you ever used those practices? {.unlisted}

```{r os8.6a}
plot_frequenze("8.6", "Open Data ")
```

## Have you ever used those practices? {.unlisted}

```{r os8.6b}
plot_confronto_gruppi("8.6", "Open Data")
```

## Can those practices contribute to the progress of the discipline? {.unlisted}

```{r os9.1a}
plot_likert_molto("9.1", "Pre-registration of Hypotheses")
```

## Can those practices contribute to the progress of the discipline? {.unlisted}

```{r os9.1b}
plot_likert_gruppi_molto("9.1", "Pre-registration of Hypotheses")
```

## Can those practices contribute to the progress of the discipline? {.unlisted}

```{r os9.2a}
plot_likert_molto("9.2", "Pre-registration of Analyses")
```

## Can those practices contribute to the progress of the discipline? {.unlisted}

```{r os9.2b}
plot_likert_gruppi_molto("9.2", "Pre-registration of Analyses")
```

## Can those practices contribute to the progress of the discipline? {.unlisted}

```{r os9.3a}
plot_likert_molto("9.3", "Registered Report ")
```

## Can those practices contribute to the progress of the discipline? {.unlisted}

```{r os9.3b}
plot_likert_gruppi_molto("9.3", "Registered Report")
```


## If you decided to pre-register a study, would you need help? {.unlisted}

```{r mrb12.1a}
plot_likert_completamente("12.1", "")
```

## If you decided to pre-register a study, would you need help? {.unlisted}

```{r mrb12.1b}
plot_likert_gruppi_completamente("12.1", "")
```

## If you decided to pre-register a study, would you feel more confident after consulting the MRB? {.unlisted}


```{r mrb12.2a}
plot_likert_completamente("12.2", "")
```

## If you decided to pre-register a study, would you feel more confident after consulting the MRB? {.unlisted}

```{r mrb12.2b}
plot_likert_gruppi_completamente("12.2", "")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.1a}
plot_likert_completamente("13.1", "Being a methodological point of reference")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.1b}
plot_likert_gruppi_completamente("13.1", "Being a methodological point of reference")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.2a}
plot_likert_completamente("13.2", "Promoting collaboration")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.2b}
plot_likert_gruppi_completamente("13.2", "Promoting collaboration")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.3a}
plot_likert_completamente("13.3", "Preventing waste")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.3b}
plot_likert_gruppi_completamente("13.3", "Preventing waste")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.4a}
plot_likert_completamente("13.4", "Improving research quality")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.4b}
plot_likert_gruppi_completamente("13.4", "Improving research quality")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.5a}
plot_likert_completamente("13.5", "Promoting good practices")
```

## How much would a MRB be useful for: {.unlisted}

```{r mrb13.5b}
plot_likert_gruppi_completamente("13.5", "Promoting good practices")
```

## To wrap up {.smaller}

- ECRs tended to attribute greater importance to the possible causes of the replication crisis

- Most respondents were familiar with Open Science practices

- Open materials and open data were used more frequently than pre-registration of hypotheses or analyses.

- Overall, most researchers felt that these practices are important 

- Not everyone expressed a need for a MRB, but many indicated interest and potential willingness to engage with it.

## Time for Feedback! 

- How could we improve people's interest in the MRB?

- What incentives can be given to reviewers?

- Should going through the MRB be mandatory?

- If so, how can it be implemented without researchers feeling threatened? 

